\texttt{vqtl}: An \texttt{R} package for Mean-Variance QTL Mapping

### 2018-04-29 Package_vqt_Manuscript.tex
minor

% \usepackage[margin = 1in]{geometry}

% \usepackage[style=authoryear,natbib=true]{biblatex}
% \bibliography{../../bibtex/10_Aim1.bib}

% \usepackage{amsmath}
% \usepackage{bm}
% \usepackage{tabu}
% \usepackage{graphicx}
% \usepackage{caption}
% \usepackage{subcaption}

% \input{styles/Corty2015commands}

@@

    \caption{
        \texttt{mean\_var\_plot}s show the estimated genotype effects at a locus with mean effects on the horizontal axis and variance effects on the vertical axis.
        Horizontal lines indicate standard errors for mean effects and vertical lines indicate standard errors for variance effects.
        For \texttt{phenotype1}, the pattern of overlapping estimates and standard errors is consistent with the fact that there are no genetic effects, and the $p$-value was not statistically significant at any locus.
        For \texttt{phenotype2}, the pattern of horizontal, but not vertical, separation visually illustrates the identified mQTL.
        For \texttt{phenotype3}, the pattern of vertical, but not horizontal, separation visually illustrates the identified vQTL.
        For \texttt{phenotype4}, the pattern of two dimensional separation without either total horizontal or vertical separation illustrates an mvQTL with neither mean nor variance effect strong enough to define an mQTL or vQTL.
        \label{fig:mean_var_plots}
    }
\end{figure}

>>>>

@@

    \caption{
        \texttt{mean\_var\_plot}s show the estimated genotype effects at a locus with mean effects on the horizontal axis and variance effects on the vertical axis.
        Horizontal lines indicate standard errors for mean effects and vertical lines indicate standard errors for variance effects.
        For \texttt{phenotype1}, the pattern of overlapping estimates and standard errors is consistent with the fact that there are no genetic effects, and the $p$-value was not statistically significant at any locus.
        For \texttt{phenotype2}, the pattern of horizontal, but not vertical, separation visually illustrates the identified mQTL.
        For \texttt{phenotype3}, the pattern of vertical, but not horizontal, separation visually illustrates the identified vQTL.
        For \texttt{phenotype4}, the pattern of two-dimensional separation illustrates an mvQTL.
        \label{fig:mean_var_plots}
    }
\end{figure}
